\vspace{0.5cm}
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}
\centerline{\xiaoerhao \textbf{[Abstract]}}
\vspace{0.5cm}

In this paper, we present Hearthstone: Heroes of Warcraft, a famous online card game, as an interesting test bed for AI research. Hearthstone has already released over 700 different kinds of cards. All these cards change the rules of the game to some extent, which causes developing a completed AI for this game extremely difficult (though this paper only takes into account a very small amount of all these Hearthstone cards), not to consider the stochastic and imperfect information characteristics of the game.

We discuss how to use Monte Carlo Search to develop AI player for Hearthstone. Monte Carlo Search has always been a classic algorithm in the field of AI research, as its descendant -- Monte Carlo Tree Search -- being the major component of the famous Go AI player -- AlphaGo. As a search algorithm, Monte Carlo Search guarantees to return an temporarily-optimal result at any moment in time, while allowing the algorithm to run for longer period often improves the result. Additionally, Monte Carlo Search is aheuristic -- the lack of domain-specific knowledge cannot prevent it from finding the optimal result.

For the experiment, we construct three different AI players for Hearthstone, being complete-random AI, rule-based AI and Monte Carlo AI respectively. Games between different AI players will be carried out to demonstrate the strength of these players. Heuristic optimizations will also be added to the Monte Carlo AI to examine if the additional domain-specific knowledge can improve the performance of Monte Carlo AI.

\par\setlength\parindent{0em}\textbf{[Keywords]}: Artificial Intelligence; Monte Carlo Search; Monte Carlo Tree Search; Hearthstone
\par\setlength\parindent{2em}
